Figure 3 - ChIP

### 2024-08-06 ms_figure_3_chip.Rmd
remove zas1 from Atf1 TF network; relabel panels of Fig3

We exclude the `untagged` experiment, TFs without targets and for the overall
network also the TFs `zas1` and `SPCC320.03`. `zas1` has
`r sum(mprom["zas1", ] > 0)` bound TFs in its promoter, and `SPCC320.03` has
`r sum(mprom["SPCC320.03", ] > 0)`, and if these were included, the network
would be hard to visualize clearly.

@@

For clearer visualization, we create a sub-network including only the
connections to and from `Atf1` (but now also including `zas1` and
`SPCC320.03`):

@@

## Create graph
## ... select TFs
to_remove <- c("untagged")
sel_tfs <- setdiff(unique(rownames(mprom), colnames(mprom)), to_remove)

@@

    ggr2 <- ggraph(as_tbl_graph(gr2), 
                   layout = as.matrix(coordsAtf1[, c("x", "y")]))
} else {
    # create graph using automated layout
    set.seed(234)
    ggr2 <- ggraph(as_tbl_graph(gr2), 
                   layout = "igraph", algorithm = "fr")

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            hm_prom_bound,
            cowplot::plot_grid(gnmtracks1, scale = 0.9),
            nrow = 2,
            labels = c("A", "B"),
            rel_heights = c(0.75, 1)
        ),
        ggr2,
        nrow = 1,
        labels = c("", "C")
    ),
    cowplot::plot_grid(
        hm_motifs_small,
        cowplot::plot_grid(
            motifs_aligned, upsets_aligned,
            nrow = 1, rel_widths = c(1.25, 1)),
        nrow = 1,
        labels = c("D", "E")
    ),
    nrow = 2,
    labels = c("", ""),
    rel_heights = c(1.75 * (w_peaksHm + 10), w_peaksHm + 20)
)
```

>>>>

We exclude the `untagged` experiment, TFs without targets and for the overall
network also the TFs `zas1` and `SPCC320.03`. `zas1` has
`r sum(mprom["zas1", ] > 0)` bound TFs in its promoter (likely an artifact),
and `SPCC320.03` has `r sum(mprom["SPCC320.03", ] > 0)`, and if these were
included, the network would be hard to visualize clearly.

@@

For clearer visualization, we create a sub-network including only the
connections to and from `Atf1` (but now also including `SPCC320.03`):

@@

## Create graph
## ... select TFs
to_remove <- c("zas1", "untagged")
sel_tfs <- setdiff(unique(rownames(mprom), colnames(mprom)), to_remove)

@@

    ggr2 <- ggraph(
        as_tbl_graph(gr2), 
        layout = as.matrix(coordsAtf1[match(names(V(gr2)), coordsAtf1$id), c("x", "y")]))
} else {
    # create graph using automated layout
    set.seed(234)
    ggr2 <- ggraph(as_tbl_graph(gr2), 
                   layout = "igraph", algorithm = "fr")

@@

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            hm_prom_bound,
            cowplot::plot_grid(gnmtracks1, scale = 0.9),
            nrow = 2,
            labels = c("A", "C"),
            rel_heights = c(0.75, 1)
        ),
        ggr2,
        nrow = 1,
        labels = c("", "B")
    ),
    cowplot::plot_grid(
        hm_motifs_small,
        cowplot::plot_grid(
            motifs_aligned, upsets_aligned,
            nrow = 1, rel_widths = c(1.25, 1)),
        nrow = 1,
        labels = c("D", "E")
    ),
    nrow = 2,
    labels = c("", ""),
    rel_heights = c(1.75 * (w_peaksHm + 10), w_peaksHm + 20)
)
```
